---
title: "Homework 2"
author: "Yihan Feng"
date: "9/27/2020"
output: github_document
---

This is my solution to Homework 2

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(dplyr)
```

# Problem 1

## Read the Mr. Trashwheel dataset. 

```{r}
trashwheel_df = 
  read_xlsx(
    "./dataset/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "Mr. Trash Wheel",     # only take the "Mr. Trash Wheel" sheet
    range = cell_cols("A:N")) %>%
  janitor::clean_names() %>%
  drop_na(dumpster) %>%
  mutate(
    sports_balls = round(sports_balls),
    sports_balls = as.integer(sports_balls)
  )
```

## Read 2018 and 2017 precipitation data.

```{r}
precip_2018 =
  read_xlsx(
    "./dataset/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2018 Precipitation",
    skip = 1      # means skip the first row
  ) %>%
  janitor::clean_names() %>%
  drop_na(month) %>%
  mutate(year = 2018) %>%
  relocate(year)
  

  precip_2017 =
  read_xlsx(
    "./dataset/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2017 Precipitation",
    skip = 1      # means skip the first row
  ) %>%
  janitor::clean_names() %>%
  drop_na(month) %>%
  mutate(year = 2017) %>%
  relocate(year)
```

## Combine 2017 and 2018 annual precipitation.

```{r}
month_df = tibble(
  month = 1:12,
  month_name = month.name
)

precip_df = 
  bind_rows(precip_2018, precip_2017)

left_join(precip_df, month_df, by = "month")
```

## Data description

This dataset contains information from the Mr. Trashwheel trash collector in Baltimore, Maryland. As trash enters the inner harbor, the trashwheel collects that trash, and stores it in a dumpster. The dataset contains information on year, month, and trash collected, include some specific kinds of trash. There are a total of `r nrow(trashwheel_df)` rows in our final dataset. Additional data sheets include monthly precipitation data. 

The total precipitation data in 2018 is `r sum(pull(precip_2018, total))` inches. And the median number of sports balls in a dumpster in 2017 is `r median(pull(precip_2017, total))` inches. 



# Problem 2

## Read and clean the NYC transit dataset. 

```{r}
transit_df = 
  read_csv("./dataset/NYC_Transit_Subway_Entrance_And_Exit_Data.csv") %>%
  janitor::clean_names() %>%
  select(line:entry, vending, ada) %>% 
  mutate(entry = ifelse(entry == "YES", yes = TRUE, no = FALSE))
```


## Dataset description

This dataset contains information of transit system of New York City, NY. The dataset contains information on line, station, routes' name and number, and ADA compliance. For dataset cleaning, I change variable names to snake case, and then select interested variables. I also convert the entry variable to a logical variable. The resulting dataset has `r nrow(transit_df)` rows and `r ncol(transit_df)` columns, yet this dataset is still not tidy enough so far. 


## Calculate number of distinct stations. 

```{r}
transit_distinct = distinct(transit_df, station_name, line)
```

There are `r nrow(transit_distinct)` distinct stations. 


## Calculate number of ADA compliant stations. 

```{r}
transit_ada = transit_df %>%
  filter(ada == "TRUE") %>%
  distinct(station_name, line)
```

There are `r nrow(transit_ada)` ADA compliant stations. 


## Calculate proportion of station entrances/exits without vending. 

```{r}
transit_distinct_number = nrow(transit_distinct)

transit_vending = transit_df %>%
  filter(entry == "TRUE", vending == "NO") %>%
  distinct(station_name, line)
transit_vending_number = nrow(transit_vending)

transit_vending_prop = transit_vending_number/transit_distinct_number
```

There are `r transit_vending_prop` proportion of station entrances/exits without vending. 


## Reformat data so that route number and route name are distinct variables. 

```{r}
transit_reformat = transit_df %>%
  mutate_at(vars(route1 : route11), as.character)%>%
  pivot_longer(
    route1 : route11,
    names_to = "route_name",
    names_prefix = "route",
    values_to = "route_number") %>%
drop_na(route_number)
```

## Calculate number of distinct stations serve the A train

```{r}
transit_atrain = transit_reformat %>%
  filter(route_number == "A") %>%
  distinct(station_name, line)
```

There are `r nrow(transit_atrain)` stations serve the A train. 

## Of the stations that serve the A train, calculate the number of ADA compliant. 

```{r}
transit_ada_atrain = transit_reformat %>%
  filter(route_number == "A", ada == "TRUE") %>%
  distinct(station_name, line)
```

There are `r nrow(transit_ada_atrain)` stations serve the A train with ADA compliant. 
















