---
title: "Homework 2"
author: "Yihan Feng"
date: "9/27/2020"
output: github_document
---

This is my solution to Homework 2

```{r setup, include=FALSE}
library(tidyverse)
library(readxl)
library(dplyr)
```

# Problem 1

## Read the Mr. Trashwheel dataset. 

```{r}
trashwheel_df = 
  read_xlsx(
    "./dataset/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "Mr. Trash Wheel",     # only take the "Mr. Trash Wheel" sheet
    range = cell_cols("A:N")) %>%
  janitor::clean_names() %>%
  drop_na(dumpster) %>%
  mutate(
    sports_balls = round(sports_balls),
    sports_balls = as.integer(sports_balls)
  )
```

## Read 2018 and 2017 precipitation data.

```{r}
precip_2018 =
  read_xlsx(
    "./dataset/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2018 Precipitation",
    skip = 1      # means skip the first row
  ) %>%
  janitor::clean_names() %>%
  drop_na(month) %>%
  mutate(year = 2018) %>%
  relocate(year)
  

  precip_2017 =
  read_xlsx(
    "./dataset/Trash-Wheel-Collection-Totals-8-6-19.xlsx",
    sheet = "2017 Precipitation",
    skip = 1      # means skip the first row
  ) %>%
  janitor::clean_names() %>%
  drop_na(month) %>%
  mutate(year = 2017) %>%
  relocate(year)
```

## Combine 2017 and 2018 annual precipitation.

```{r}
month_df = tibble(
  month = 1:12,
  month_name = month.name
)

precip_df = 
  bind_rows(precip_2018, precip_2017)

left_join(precip_df, month_df, by = "month")
```

## Data description

This dataset contains information from the Mr. Trashwheel trash collector in Baltimore, Maryland. As trash enters the inner harbor, the trashwheel collects that trash, and stores it in a dumpster. the dataset contains information on year, month, and trash collected, include some specific kinds of trash. There are a total of `r nrow(trashwheel_df)` rows in our final dataset. Additional data sheets include monthly precipitation data. 










